### 2017-04-17 paper/oopsla17-submission/evaluation-utility.tex
forgot to account for list-literal feature

\mysubsection{Feature Utility}
\label{sec:feature-utility}
We have shown that we can train a classifier to effectively localize
type errors, but which of the feature classes from
\autoref{sec:features} are contributing the most to our accuracy?
%
We focus specifically on feature \emph{classes} rather than individual
features as our 277 features are conceptually grouped into a much
smaller number of \emph{categorical} features.
%
For example, the syntactic class of an expression is conceptually a
feature but there are 44 possible values it could take; to encode this
feature for learning we split it into 44 distinct binary features.
%
Analyses that focus on individual features, \eg \textsc{ANOVA},
are difficult to interpret in our setting, as they will tell us the
importance of the binary features but not the higher-level categorical
features.
%
Thus, to answer our question we investigate the performance of
classifiers trained on various subsets of the feature classes.

@@

As one might expect, the typing features are more beneficial than the
contextual syntactic features.
%
They improve Top-1 accuracy by an additional 2\%, and are much more
compact --- requiring only 55 typing features compared to 176
contextual syntactic features.
%
This aligns with our intuition that types should be a good summary of
the context of an expression.
%
However, typing features do not appear to \emph{subsume} contextual
syntactic features, the \hiddenFH gains an additional 4\% Top-1 accuracy
when both are added.

>>>>

\mysubsection{Feature Utility}
\label{sec:feature-utility}
We have shown that we can train a classifier to effectively localize
type errors, but which of the feature classes from
\autoref{sec:features} are contributing the most to our accuracy?
%
We focus specifically on feature \emph{classes} rather than individual
features as our 282 features are conceptually grouped into a much
smaller number of \emph{categorical} features.
%
For example, the syntactic class of an expression is conceptually a
feature but there are 45 possible values it could take; to encode this
feature for learning we split it into 45 distinct binary features.
%
Analyses that focus on individual features, \eg \textsc{ANOVA},
are difficult to interpret in our setting, as they will tell us the
importance of the binary features but not the higher-level categorical
features.
%
Thus, to answer our question we investigate the performance of
classifiers trained on various subsets of the feature classes.

@@

As one might expect, the typing features are more beneficial than the
contextual syntactic features.
%
They improve Top-1 accuracy by an additional 2\%, and are much more
compact --- requiring only 55 typing features compared to 180
contextual syntactic features.
%
This aligns with our intuition that types should be a good summary of
the context of an expression.
%
However, typing features do not appear to \emph{subsume} contextual
syntactic features, the \hiddenFH gains an additional 4\% Top-1 accuracy
when both are added.
